Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-17 sections/introduction.tex
changed text to match new figures

\begin{figure}
  \sidecaption[t]
  \includegraphics{gr/intro/Fig_SICM-resolution}
  \caption{\textbf{Resolution of SICM.} \textbf{a:} Height profiles (plotted
    vertically) of modelled SICM recordings of two cilindrical particles
    (height and diameter: $r_\text{i}$) at varying distances. \textbf{b:} Two
    consecutive SICM recordings of the equatorial segment of a living boar
    spermatozoon recorded 10 minutes apart with a scanning pipette with
    $r_\mathrm{i} \approx 6.75\,\text{nm}$. \textbf{a:} reprinted with
    permission from ref. \cite{rheinlaender:094905}, \textbf{b:} reprinted
    with permission from ref. \cite{Shevchuk2006}. 
  }
  \label{fig:sicm-resolution}
\end{figure}

The resolution of SICM is determined by the inner opening radius
$r_\mathrm{i}$ of the scanning pipette and can be approximated as
$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}a)
\cite{rheinlaender:094905,Rheinlaender2015}.  Thus, the resolution of SICM is
only limited by the technical limits to produce pipettes with very small
openings. Pipettes with radii of approximately 6.75\,nm have been used in for
SICM imaging (Fig.~\ref{fig:sicm-resolution}b) \cite{Shevchuk2006}. In
contrast, the resolution in light microscopy is fundamentally limited by the
diffraction of light. As Ernst Abbe found out in 1873, a beam of light cannot
be focused to a spot smaller than the resolution limit $d_\text{min}$
\cite{Abbe1873}:
\begin{equation}
  d_\text{min} = \frac\lambda{2n\sin\alpha} = \frac\lambda{2\mathrm{NA}}\text{.}
  \label{eq:diffraction-limit}
\end{equation}
Here, $\lambda$ denotes the wavelength of the light used to generate the
image, $n$ the diffractive index of the medium between sample and objective
lense and $\alpha$ the half-cone opening angle of the objective lense. The
product $n\sin\alpha$ is called the numerical aperture $\mathrm{NA}$ of the
objective. The exact limit, of course, depends on $\lambda$ and the NA of the
objective, but as a rule of thumb, it is often stated that the resolution
limit is in the range of 200\,nm. This is approximately 14 times the size of
the smallest structures observed in the SICM recordings shown in
Fig.~\ref{fig:sicm-resolution}B, which were reported to be 14\,nm
\cite{Shevchuk2006}.

\begin{figure}
  \sidecaption
  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
      spermatozoon.} \textbf{a:} Proteins A and B in the stable structures
    observed by SICM. \textbf{b:} Hypothetical positions of the fluorescent
    labels of proteins A and B. Scale bar: 200\,nm \textbf{c:} Computed
    fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm
    for the green marker.}
  \label{fig:sicm-and-light-resolution}
\end{figure}
In all stable structures in the recordings (highlighted by the dashed lines)
at least one group of three protrusions arranged in a line are observable. To
exemplify the impact of the limited resolution of light microscopy, assume,
without any biological support, that such a complex is comprised of two
different proteins A and B, which float in the plasma membrane until they form
the complex. In the complex, protein A is located at the first and last
position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and
protein B on the central spot (green arrows in
Fig.~\ref{fig:sicm-and-light-resolution}a). Further, assume that the two
different proteins have been labelled by two different fluorescent markers
(the positions of the markers are indicated by the magenta and green dots in
Fig.~\ref{fig:sicm-and-light-resolution}b) and a correlating light microscopic
image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}c) to analyze
the molecular composition of the stable structures.

Due to the limited resolution, the fluorescence image consists of overlapping
spots of the two different markers and looks blurred, compared to the
SICM topography image. Although co-localisation of the two proteins can be
observed at the positions of the stable structures, it is hard if not
impossible to allocate the fluorescent spots to protrusions in the topography
image.

>>>>

\begin{figure}\centering
  \includegraphics{gr/intro/Fig_SICM-resolution}
  \caption{\textbf{Resolution of SICM.}  \textbf{a:} Height profiles
    (plotted vertically) of modelled SICM recordings of two cilindrical
    particles (height and diameter: $r_\text{i}$) at varying
    distances. \textbf{b:} Apparent height of the particles (solid line) and of
    the gap between them (dahsed line) as determined by SICM. At distances
    $d\lessapprox3r_\text{i}$, no gap between the particles is detected.
    Reprinted from Johannes Rheinlaender, Tilman E. Schäffer: \emph{Image
      formation, resolution, and height measurement in scanning ion
      conductance microscopy}, Journal of Applied Physics 2009, 105(9), with
    the permission of AIP Publishing.  }
  \label{fig:sicm-resolution}
\end{figure}

The resolution of SICM is determined by the inner opening radius
$r_\mathrm{i}$ of the scanning pipette and can be approximated as
$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}a)
\cite{rheinlaender:094905,Rheinlaender2015}.  Thus, the resolution of SICM is
only limited by the technical limits to produce pipettes with very small
openings. Pipettes with radii of approximately 6.75\,nm have been used in for
SICM imaging \cite{Shevchuk2006}. In
contrast, the resolution in light microscopy is fundamentally limited by the
diffraction of light. As Ernst Abbe found out in 1873, a beam of light cannot
be focused to a spot smaller than the resolution limit $d_\text{min}$
\cite{Abbe1873}:
\begin{equation}
  d_\text{min} = \frac\lambda{2n\sin\alpha} = \frac\lambda{2\mathrm{NA}}\text{.}
  \label{eq:diffraction-limit}
\end{equation}
Here, $\lambda$ denotes the wavelength of the light used to generate the
image, $n$ the diffractive index of the medium between sample and objective
lense and $\alpha$ the half-cone opening angle of the objective lense. The
product $n\sin\alpha$ is called the numerical aperture $\mathrm{NA}$ of the
objective. The exact limit, of course, depends on $\lambda$ and the NA of the
objective, but as a rule of thumb, it is often stated that the resolution
limit is in the range of 200\,nm. This is approximately 14 times the size of
the smallest structures observed in the SICM recordings, which were reported to be 14\,nm
\cite{Shevchuk2006}.

\begin{figure}
  \centering
  \includegraphics{gr/intro/effect-of-resolution}%
  \caption{\textbf{Hypothetical fluorescence analysis of a protein forming
      membrane protrusions.} \textbf{a:} SICM recording of membrane protrusion
    and location of a putative protein within it. \textbf{b:} Computed
    diffraction limited fluorescence recording of the protein with a resolution
    of 250\,nm. \textbf{c:} Computed
    diffraction unlimited fluorescence recording of the protein with a
    resolution of 75\,nm.}
  \label{fig:sicm-and-light-resolution}
\end{figure}

To exemplify the impact of the limited resolution of light microscopy, assume,
without any biological support, that a cellular protrusion as shown in
Fig.~\ref{fig:sicm-and-light-resolution}a is formed by a protein (black line
in Fig.~\ref{fig:sicm-and-light-resolution}a). A -- hypothetical --
diffraction limited recording of that protein would only show a blurred spot
(Fig.~\ref{fig:sicm-and-light-resolution}b), while a recording with an
improved resolution would clearly allow to see that the location of the
protein correlates with the position of the protrusion
(Fig.~\ref{fig:sicm-and-light-resolution}c).
